Network Configuration Synthesis with Abstract Topologies

### 2016-11-10 paper/abstraction/paper.tex
update concretization proof with new definitions

Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract compilation. Notably, the abstract analysis takes the majority of the time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost. In particular, the number of calls to Z3 remains constant the across topology size. The seesaw behavior for the data center networks results from differences in time taken by Z3 to minimize the same constraints with different parameters.

>>>>

Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract compilation. Notably, the abstract analysis takes the majority of the time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost. In particular, the number of calls to $\nu$Z remains constant the across topology size. The seesaw behavior for the data center networks results from differences in time taken by $\nu$Z to minimize the same constraints with different parameters.
